---
title: "Learning Rmarkdown"
author: "Edmond Kwan"
date: "2020-11-16"
output:
  html_document:
    toc: True
    toc_depth: 2
    theme: readable
    code_folding: "hide"

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(magrittr)
library(dplyr)
library(DT)
library(ggplot2)
```


# Introduction

> outcomes:

- Learn how to creat and share Rmarkdown document
- Learn various document types, e.g. html, pdf and docx
- ~~Learn to fly the rocket!~~

The bottom line is - I would like to learn Rmarkdown!
<br>
Like **seriously** become **good** at it !  
Like **seriously** become **good** at it !  

## Task list for today

- [X] Get aspired to learn Rmarkdown
- [ ] Get to know three core components of the Rmarkdown document (header, body, R chunks)
- [ ] Practice, practice, practice!  

## Code

```{r examine_packages}
library(magrittr)

avail_packages <- available.packages(contriburl = contrib.url("https://mirror.aarnet.edu.au/pub/CRAN/"))

#head(avail_packages)
```

### Getting and wrangling the data


```{r get_data, echo=FALSE}

library(magrittr)
library(dplyr)

avail_packages <- available.packages(contriburl = contrib.url("https://mirror.aarnet.edu.au/pub/CRAN/")) %>% 
                    as.data.frame() %>% 
                    as_tibble() %>% 
                    rowwise() %>% 
                    mutate(Depend = length(unlist(strsplit(Imports, split = ",")))) %>% 
                    ungroup() %>% 
                    select(Package, Version, Depend, Imports, License)
```


```{r make_table, message=FALSE, warning=FALSE}
library(DT)
avail_packages %>% datatable(escape = FALSE)
```


## Plot the data

```{r plot}
library(ggplot2)
avail_packages %>% ggplot(aes(Depend)) + geom_bar()
```

